Biden Expected to Win 54% of Popular Vote in 2020 US Presidential Election

### 2020-11-03 outputs/paper/paper.Rmd
added discussion for age and gender

# Discussion

>>>>

# Discussion
Figure 1 features the trend of the younger voters (between the ages of 18 and 38) to vote left-wing. There are many different reasons this can be the case. Younger people generally tend to be left wing (pew 1). In addition, given the current state of the economy, combined with the fact that in general millennials and Gen-Xers are poorer than their parents, many younger voters are in disillusion with the current government, leading to vote against the Republican Party (mckinsey).

Regardless of the reason most young voters support Biden, it’s imperative to realize the repercussions of this. Relative to the 2016 election, young voters are coming out (metaphorically) in droves to vote, be it due to their own stronger opinions, voting drives and increased voting awareness online, or any other facet of their lives. In Texas alone, 1.3 million voters under 30 have already cast their ballot, surpassing the TOTAL number of young votes from 2016 (Texas). This can have huge effects nationally, creating a greater likelihood of a Biden victory.

Contrasting this are the older populations. The majority of voters ages 49 and above support Trump. However, a key point of note is that the difference between Biden support and Trump support is much lower than with younger voters. Given this, there’s not as much change in the way of Trump. That said, in typical elections this does indeed make a huge difference regardless, as it’s the older voters that vote the most (old). That’s why it’s so important that many young voters are actually voting compared to before, as this drive to vote acts a form of mitigation against the older voters’ support of Trump.

•	https://www.pewresearch.org/fact-tank/2014/07/09/the-politics-of-american-generations-how-age-affects-attitudes-and-voting-behavior/
•	https://www.texasobserver.org/young-voters-texas-2020/
•	https://www.mckinsey.com/featured-insights/employment-and-growth/poorer-than-their-parents-a-new-perspective-on-income-inequality#
•	https://pubmed.ncbi.nlm.nih.gov/10750310/

Figure 2’s comparison of the votes by gender reveals some interesting findings. While the majority of male voters support Trump, the real highlight of this figure is the fact that nearly 60% of female voters support Biden, essentially twice the difference between Biden and Trump for male voters. Again, there’s many reasons why this could be the case, but there are two major reasons that present themselves.

The first is the way that Trump has treated women in the past, a notable example being his quote “Grab ‘em by the pussy” (tape). The other reason that stands out is the Republican Party’s stance against abortion, an important women’s right issue. This has only been further exemplified with the recent nomination and appointment of Amy Coney to the supreme court, who maintains a personal belief that abortion is immoral and clerked for Justice Scalia, who was a major critic of Roe v. Wade, the case that set the legal precedent for abortion (bbc).

Overall, while there in majority men vote support Trump, a greater percentage of women support Biden. In conjunction with the metric that women vote more than man, this finding supports a Biden victory. (gender diff)

•	https://www.nytimes.com/2016/10/08/us/donald-trump-tape-transcript.html
•	https://www.bbc.com/news/election-us-2020-54512678
•	https://cawp.rutgers.edu/sites/default/files/resources/genderdiff.pdf
